Supplementary material for\\ A Benchmark of Named Entity Recognition Approaches in Historical Documents\\ Application to 19$^{th}$ Century French Directories

### 2022-01-20 src-latex/parts/30-dataset.tex
Updates from Overleaf

The directories to be processed are stored in different libraries in Paris. They have been scanned independently and with various levels of quality. Moreover, they cover a wide period and have been produced by different publishers and printers. Therefore, their contents, indexes, layouts, methods of printing, etc. may vary a lot from one directory to another (see Figure \ref{fig:directories}). For training and testing purposes, our groundtruth dataset must be as representative as possible of the diversity of the available directories.

@@

For example, the Didot directory of 1854 is organised according to three indexes: by name, by activity, and by street name. The structure of the following entry is characteristic of its index by name: "Batton (D.-A.) \scalerel*{\includegraphics{./images/LH.png}}{H}, professeur au Conservatoire de musique et de déclamation, Saint-Georges, 47." This entry begins with a person's name, followed by the initials of their first name in parentheses.The symbol indicates that this person was awarded the Légion d'Honneur. The following part of this entry represents the person's activity,i.e., their profession, or social status, here "professor at the Conservatory of music and declamation". The street name and number where the person lives or carries out their activities are written at the end of the entry.

These pieces of information stored in the entries are the basic data that we want to extract, deduplicate, and structure to build a spatio-temporal database of XIX\textsuperscript{th} century Parisian inhabitants and businesses. Except for some potentially wordy activity descriptions, they correspond to named entities. However, while most entries contain the same types of named entities, their order and the way they are written vary from one directory/index to another. To provide examples of each entry structure, pages from each type have thus been annotated. %\footnote{In this work, the street name index entries have not been included as they are very different from the others. The strategy to be adopted to process them without loss of quality for the NER model will be the subject of future work.}.

@@

\textbf{NER Q.A.}. The NER system outputs a text with tags that enclose the entities. To assess the quality of the
entity extraction, we rely on a technique similar as for the OCR evaluation to build the \emph{NER-target}. The
\emph{NER-target} is different from the groundtruth because it should not involve the errors committed during the
previous stages. The OCR text is first aligned with the groundtruth text to form the NER-\emph{input} (where
\emph{input} is a placeholder for \emph{pero} if the input text is from PERO, NER-\emph{tesseract},
NER-\emph{reference}\ldots). The tags of the groundtruth are then projected in the alignment on NER-\emph{input} to
provide the \emph{NER-target}. The NER system then runs on NER-\emph{input} and outputs the \emph{NER-prediction}. The
precision, recall, and f-measure (or f-score) are computed considering only the exact matches between entities of the
\emph{NER-target} and those from the \emph{NER-prediction}, i.e. pairs of entries for which the type, start and end positions are exactly the same.
Precision is the ratio of exactly matches divided by the number of predicted entries,
and recall is defined as the ratio of exact matches divided by the number of expected entries;
the f-measure is their harmonic mean.

The evaluation process illustrated on~\cref{fig.eval-ocr-ner}. The OCR text and the groundtruth are first aligned to
evaluate the OCR accuracy. As there are 11 mismatches over 56 aligned characters, the CER is thus 24\%. This alignment
is then used to back-project the groundtruth tags to build the tagged NER-\emph{target}. Finally, the NER system runs on the
OCR text; its output is compared to the NER groundtruth. There is only 2 over 3 tags matching in the prediction (precision),
while only 2 over 4 entities are matched in the reference (recall). It follows an overall f-score of 0.4.
%
A side-effect of tag projections is that is can produce degenerated tags, i.e. empty or containing only spaces.
In such cases, the corresponding entries must be removed from the dataset for NER evaluation,
and only the intersection of the sets of valid entries must be used to compare NER systems on multiple OCR predictions or references.

>>>>

The directories are available from different libraries in Paris and have been digitised independently in various levels of quality. 
They cover a large period of time and originate from several publishers.
Therefore, their contents, indexes, layouts, methods of printing, etc. may vary a lot from one directory to another (see Figure \ref{fig:directories}).
We want our groundtruth dataset to be representative of the diversity of directories available on the period.

@@

Directories contain lists of people with various information attached.
For instance the directory published by \emph{Didot} in 1854 contains three redundant lists or people sorted by name, by activity and by street name.
An typical example entry from this directory is "Batton (D.-A.) \scalerel*{\includegraphics{./images/LH.png}}{H}, professeur au Conservatoire de musique et de déclamation, Saint-Georges, 47.":  it begins with the person's name and surname (here in parentheses).
The glyph denotes that this person was awarded the Légion d'Honneur.
Then comes a descriptions of the person's activity, here his profession (professor at the Conservatory of music and declamation), but it can also be a social status.
Such descriptions range from a single word to paragraphs describing the occupation in full detail.
The street name and number where the person lives or carries out their activities ends the entry.

These are the structured data that we want to extract, deduplicate  and structure to build a spatio-temporal database.
Except for some potentially wordy activity descriptions, they correspond to named entities. However, while most entries contain the same types of named entities, their order and the way they are written vary from one directory/index to another. To provide examples of each entry structure, pages from each type have thus been annotated. %\footnote{In this work, the street name index entries have not been included as they are very different from the others. The strategy to be adopted to process them without loss of quality for the NER model will be the subject of future work.}.

@@

\textbf{NER Q.A.}. The NER system outputs a text with tags that enclose the entities. To assess the quality of the
entity extraction, we rely on a technique similar as for the OCR evaluation to build the \emph{NER-target}. The
\emph{NER-target} is different from the groundtruth because it should not involve the errors committed during the
previous stages. The OCR text is first aligned with the groundtruth text to form the NER-\emph{input} (where
\emph{input} is a placeholder for \emph{pero} if the input text is from PERO, NER-\emph{tesseract},
NER-\emph{reference}\ldots). The tags of the groundtruth are then projected in the alignment on NER-\emph{input} to
provide the \emph{NER-target}. The NER system then runs on NER-\emph{input} and outputs the \emph{NER-prediction}. The
precision, recall, and f-measure (or f-score) are computed considering only the exact matches between entities of the
\emph{NER-target} and those from the \emph{NER-prediction}, i.e. pairs of entries for which the type, start and end positions are exactly the same.
Precision is the ratio of exact matches divided by the number of predicted entries,
and recall is defined as the ratio of exact matches divided by the number of expected entries;
the f-measure is their harmonic mean.

The evaluation process is illustrated on~\cref{fig.eval-ocr-ner}. The OCR and the groundtruth texts are first aligned to
evaluate the OCR accuracy. As there are 11 mismatches over 56 aligned characters, the CER is thus 24\%. This alignment
is then used to back-project the groundtruth tags to build the tagged NER-\emph{target}. Finally, the NER system runs on the
OCR text; its output is compared to the NER groundtruth. There is only 2 over 3 tags matching in the prediction (precision),
while only 2 over 4 entities are matched in the reference (recall). It follows an overall f-score of 0.4.
%
A side effect of tag projection is that it can produce degenerated tags, i.e. empty or containing only spaces.
In such cases, the corresponding entries must be removed from the dataset,
and only the intersection of the sets of valid entries must be used to compare NER systems with multiple OCR predictions or references.

### 2022-01-20 src-latex/parts/50-ner-xp1-training-set-size-and-pretraining.tex
Updates from Overleaf

\subsection{Training and evaluation protocol}
\label{sec:ner-xp1-protocol}
The following three models form our baseline for both NER experiments.
Their short names written in square brackets will be used to reference them from now on.
\begin{itemize}
    \item \textbf{SpaCy NER pipeline for French~[SpaCy NER]}: We use the pipeline \textit{fr\_core\_news\_lg} provided by SpaCy v.3.2.1\mcite{spacy}, already trained for NER on the french corpora deep-sequoia and wikiner-fr.
    We stress again that we use the CNN version of this pipeline, not the transformer-based available in SpaCy v3.
    \item \textbf{Huggingface CamemBERT~[CmBERT]}: We rely on the implementation of BERT models provided by the software library Huggingface (transformers v.4.15.0, datasets v.1.17.0).
We chose to reuse a CamemBERT model published on the Hugging Face repository \footnote{\url{https://huggingface.co/Jean-Baptiste/camembert-ner}} and already trained for NER on wikiner-fr.
\item \textbf{CamemBERT pretrained on Paris directories~[CmBERT+ptrn]}: 
In order to evaluate whether adapting CamemBERT to the domain increases its performances, we do an unsupervised pre-training of CmBERT for next sentence prediction and masked language modeling, using \num{845000} entries randomly sampled and OCRed with Pero.
The model is trained for 3 epochs and is available online\footnote{\url{https://huggingface.co/HueyNemud/das22-10-camembert_pretrained}}.
\end{itemize}

>>>>

\subsection{Training and evaluation protocol}
\label{sec:ner-xp1-protocol}
The following models form our baseline for both NER experiments.
Their short names written in square brackets will be used to reference them from now on.
\begin{itemize}
    \item \textbf{SpaCy NER pipeline for French~[SpaCy NER]}: We use the pipeline \textit{fr\_core\_news\_lg} provided by SpaCy v.3.2.1\mcite{spacy}, already trained for NER on the french corpora deep-sequoia and wikiner-fr.
    We stress again that we use the CNN version of this pipeline, not the transformer-based available in SpaCy v3.
    \item \textbf{Huggingface CamemBERT~[CmBERT]}: We rely on the implementation of BERT models provided by the software library Huggingface (transformers v.4.15.0, datasets v.1.17.0).
We chose to reuse a CamemBERT model published on the Huggingface repository \footnote{\url{https://huggingface.co/Jean-Baptiste/camembert-ner}} and already trained for NER on wikiner-fr.
\item \textbf{CamemBERT pretrained on Paris directories~[CmBERT+ptrn]}: 
In order to evaluate whether adapting CamemBERT to the domain increases its performances, we do an unsupervised pre-training of CmBERT for next sentence prediction and masked language modeling, using \num{845000} entries randomly sampled and OCRed with Pero.
The model is trained for 3 epochs and is available online\footnote{\url{https://huggingface.co/HueyNemud/das22-10-camembert_pretrained}}.
\end{itemize}
